### 2024-04-01 paper/content.tex
Fix captions with upward continuation results
They said that the continuation was to suppress long wavelength noise,
which it can't do.

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
  \caption{
    Complex synthetic data and the various processing steps performed prior to the dipole moment inversion.
    a) The synthetic high and low-frequency noise-corrupted $b_z$ observations at
    $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated.
    b) Anomaly map after the upward-continued data to $z = \qty{10}{\micro\meter}$ to attenuated long and short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source.
    d) The contrast-stretched TGA, highlighting the signal of all sources, especially the weaker ones.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the difference between the true and estimated
    $z$ coordinates.
  }
  \label{complex-synthetic-data}
\end{figure}

@@

\begin{figure}[ph!]
\centering
\includegraphics[width=1\linewidth]{figures/real-data.png}
\caption{Real data and the various processing steps performed prior to the dipole moment inversion.
    a) The real sample vertical component magnetic data $b_z$ observations at
    $z = \qty{5}{\um}$.
    b) Anomaly map after the upward-continued data to $z = \qty{10}{\um}$ to attenuated long and short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data.
    d) The contrast-stretched TGA.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the main signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the estimated $z$ coordinates.
  }
\label{real-data}
\end{figure}

>>>>

\begin{figure}[tb!]
  \centering
  \includegraphics[width=1\linewidth]{figures/complex-synthetic-data.png}
  \caption{
    Complex synthetic data and the various processing steps performed prior to the dipole moment inversion.
    a) The synthetic high and low-frequency noise-corrupted $b_z$ observations at
    $z = \qty{5}{\micro\meter}$ due to two clusters of stable directions simulated.
    b) Anomaly map after upward-continuation to $z = \qty{10}{\micro\meter}$ to attenuate short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data, which is able to concentrate the signal on top
    of each dipolar source.
    d) The contrast-stretched TGA, highlighting the signal of all sources, especially the weaker ones.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the difference between the true and estimated
    $z$ coordinates.
  }
  \label{complex-synthetic-data}
\end{figure}

@@

\begin{figure}[ph!]
\centering
\includegraphics[width=1\linewidth]{figures/real-data.png}
\caption{Real data and the various processing steps performed prior to the dipole moment inversion.
    a) The real sample vertical component magnetic data $b_z$ observations at
    $z = \qty{5}{\um}$.
    b) Anomaly map after upward-continuation to $z = \qty{10}{\um}$ to attenuate short-wavelength noise.
    c) The total gradient amplitude (TGA) calculated from the
    upward-continued data.
    d) The contrast-stretched TGA.
    e) The detected source bounding boxes (black squares) that correctly
    encapsulate the main signal of the sources.
    f) The estimated source locations (colored circles) from Euler
    Deconvolution of the upward-continued data inside each bounding box.
    The color represents the estimated $z$ coordinates.
  }
\label{real-data}
\end{figure}
